Follow-up Samples

### 2017-01-19 submission/manuscript_outline_20161024.Rmd

**Figure 3: Graph of the Receiver Operating Characteristic Curve for lesion and Initial and Follow up Models.** The shaded areas represents the range of values of a 100 different 80/20 splits of the test set data using either all variables (grey) or reduced variable (red) models.  The blue line represents the reduced variable model using 100% of the data set.  A) Lesion model.  B) Initial/Follow up model

**Figure 4: Breakdown by Carcinoma and Adenoma of Prediction Results for Lesion and Initial Follow Up Reduced Variable Models**  A) Lesion positive probability adjustment of those with carcinoma from initial to follow up sample  B) Initial follow up positive probability adjustment of those with carcinoma from initial to follow up sample  C) Lesion positive probability adjustment of those with adenoma as well as those with SRN and the probability adjustment from initial to follow up sample.    D) Initial follow up positive probability adjustment of those with adenoma as well as those with SRN and the probability adjustment from initial to follow up sample.  The dotted line represents the threshold used to make the decision of whether a sample was positive or not.

@@

**Figure S3: Summary of Important Variables in Initial Follow Up Model** A) MDA of the most important variables in the lesion model.  The black point represents the median and the different colors are the different runs up to 100.  B) The total number of appearances of each variable in the 100 different lesion models.  The cutoff of 50% was used to assess importance.

**Figure S4: Breakdown by Carcinoma and Adenoma of Prediction Results for Lesion and Initial and Follow Up Full Variable Models** A) Lesion positive probability adjustment of those with carcinoma from initial to follow up sample  B) Initial follow up positive probability adjustment of those with carcinoma from initial to follow up sample  C) Lesion positive probability adjustment of those with adenoma as well as those with SRN and the probability adjustment from initial to follow up sample.    D) Initial follow up positive probability adjustment of those with adenoma as well as those with SRN and the probability adjustment from initial to follow up sample.  The dotted line represents the threshold used to make the decision of whether a sample was positive or not.

>>>>

**Figure 3: Graph of the Receiver Operating Characteristic Curve for lesion and Before Sample Models.** The shaded areas represents the range of values of a 100 different 80/20 splits of the test set data using either all variables (grey) or reduced variable (red) models.  The blue line represents the reduced variable model using 100% of the data set.  A) Lesion model.  B) Defore sample model

**Figure 4: Breakdown by Carcinoma and Adenoma of Prediction Results for Lesion and Before Sample Reduced Variable Models**  A) Lesion positive probability adjustment of those with carcinoma from initial to follow up sample  B) Initial follow up positive probability adjustment of those with carcinoma from initial to follow up sample  C) Lesion positive probability adjustment of those with adenoma as well as those with SRN and the probability adjustment from initial to follow up sample.    D) Initial follow up positive probability adjustment of those with adenoma as well as those with SRN and the probability adjustment from initial to follow up sample.  The dotted line represents the threshold used to make the decision of whether a sample was positive or not.

@@

**Figure S3: Summary of Important Variables in Before Sample Model** A) MDA of the most important variables in the lesion model.  The black point represents the median and the different colors are the different runs up to 100.  B) The total number of appearances of each variable in the 100 different lesion models.  The cutoff of 50% was used to assess importance.

**Figure S4: Breakdown by Carcinoma and Adenoma of Prediction Results for Lesion and Before Sample Full Variable Models** A) Lesion positive probability adjustment of those with carcinoma from initial to follow up sample  B) Initial follow up positive probability adjustment of those with carcinoma from initial to follow up sample  C) Lesion positive probability adjustment of those with adenoma as well as those with SRN and the probability adjustment from initial to follow up sample.    D) Initial follow up positive probability adjustment of those with adenoma as well as those with SRN and the probability adjustment from initial to follow up sample.  The dotted line represents the threshold used to make the decision of whether a sample was positive or not.
